---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


```{r}
trainDat = read.csv('train_5level.csv', header = TRUE)
testDat = read.csv('test_5level.csv', header = TRUE)
# change label from 2,3,4,5,6 to 0,1,2,3,4, setting of XGB requires that
trainDat$Cannabis = trainDat$Cannabis -2
testDat$Cannabis = testDat$Cannabis -2
testDat <- na.omit(testDat)
trainDat$Cannabis <- as.character(trainDat$Cannabis)
testDat$Cannabis <- as.character(testDat$Cannabis)
```

```{r}
require(xgboost)
set.seed(1)
```

```{r}
trainDat_X = as.matrix(trainDat[,1:ncol(trainDat)-1])
trainDat_y = trainDat$Cannabis
testDat_X = as.matrix(testDat[,1:ncol(trainDat)-1])
testDat_y = testDat$Cannabis
```

```{r}
xgb.train = xgb.DMatrix(data=trainDat_X,label=trainDat_y)
xgb.test = xgb.DMatrix(data=testDat_X)
```

```{r}
num_class = length(unique(trainDat_y))
params = list(
  booster="gbtree",
  eta= c(0.01),
  min_child_weight = c(3,4,5,6),
  max_depth=c(3,4,5,6),
  gamma=c(0.1,1,2,3),
  subsample=c(0.75,0.85,0.95),
  colsample_bytree=c(1,3,5),
  objective="multi:softprob",
  eval_metric="mlogloss",
  num_class=num_class
)
```

```{r}
# Train the XGBoost classifer
set.seed(0)
xgb.fit=xgb.train(
  params=params,
  data=xgb.train,
  verbose=0,
  nrounds=1000
)

# Review the final model and results
xgb.fit
```

best model: params (as set within xgb.train):
  booster = "gbtree", eta = "0.01", min_child_weight = "3", max_depth = "4", gamma = "5", subsample = "6", colsample_bytree = "3", objective = "4", eval_metric = "5", num_class = "6", validate_parameters = "0.1", booster = "1", eta = "2", min_child_weight = "3", max_depth = "0.75", gamma = "0.85", subsample = "0.95", colsample_bytree = "1", objective = "3", eval_metric = "5", num_class = "multi:softprob", validate_parameters = "mlogloss", booster = "7", eta = "TRUE"
xgb.attributes:

```{r}
xgb.pred = predict(xgb.fit,testDat_X,reshape=T)
xgb.pred = as.data.frame(xgb.pred)
xgb.pred
```

```{r}
# num_class = 7
colnames(xgb.pred) <- c('2','3','4','5','6')
xgb.pred$prediction = apply(xgb.pred,1,function(x) colnames(xgb.pred)[which.max(x)])
xgb.pred
```

```{r}
testDat_y = as.character(as.numeric(testDat_y)+2)
result_table <- table(testDat_y, xgb.pred$prediction)
result_table
paste('Testing accuracy is:', sum(diag(result_table)) / length(testDat_y))
```











